### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yny 1115a

PI Young has been actively involved with promotion of
underrepresented students at NJIT. One PhD student, Herve Nganguia, is
now an Assistant Professor at Towson University. PI Young has taught a
broad spectrum of courses in fluid mechanics and applied math modeling.
PI Quaife will work with undergraduates and high school
students through the Undergraduate Research Opportunity Program and
Young Scholar's Program, as he has done in the past.

>>>>

PI Young has been actively involved with promotion of
underrepresented students at NJIT.  A former PhD student, Herve Nganguia, is African American and 
now an Assistant Professor at Towson University. 
%PI Young has taught a
%broad spectrum of courses in fluid mechanics and applied math modeling.
PI Quaife will continue to work with undergraduates and high school
students through the Undergraduate Research Opportunity Program and
Young Scholar's Program.
%, as he has done in the past.
